Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-05-23 cordillera-cycle.tex
Develop athosmpheric forcing method.

% Greenland Ice Core Project (GRIP)
% North Greenland Ice Core Project (NGRIP)
% European Project for Ice Coring in Antarctica (EPICA)
% Lake Vostok (Vostok)
% Ocean Drilling Program (ODP)

@@

where $\phi$ is given in degrees and $z$ in meters above current sea level.
This model thus accounts for a~weakening of till associated with the presence
of marine sediments \citep{martin-etal-2011,aschwanden-etal-2013}. Because the
distribution of marine sediments is assumed constant throughout the run, the
till friction angle $\phi$ is not affected by changes in bed elevation. Basal
topography (Fig.~\ref{fig:topo}) is derived from the ETOPO1 combined topography
and bathymetry dataset with a~resolution of 1\,arc-min \citep{data:etopo1}.

@@

Atmospheric forcing of the model consists of a present-day monthly climatology
on the one hand, and time-dependent temperature offsets on the other hand. The
present-day climatology was computed from the near-surface air temperature and
precipitation rate fields of the North American Regional Reanalysis (NARR) over
the period xxxx--xxxx.

Prior to surface mass balance computation, the model dynamically applies
a~lapse-rate correction to surface air temperature. This correction accounts
for the evolution of ice thickness on the one hand, and differences between the
climate forcing reference topography and the ice flow model basal topography on
the other hand. It uses a~reference topography distinct from the modelled basal
topography and specific to each climate forcing dataset (Fig.~\ref{fig:topo}).
An annual lapse rate of 6\,\unit{{\degree}C\,km^{-1}} is used in all
simulations. No corrections apply to precipitation changes with elevation.

>>>>

@@

where $\phi$ is given in degrees and $z$ in meters above current sea level.
This model thus accounts for a~weakening of till associated with the presence
of marine sediments \citep{martin-etal-2011,aschwanden-etal-2013}. Because the
distribution of marine sediments is assumed constant throughout the run, the
till friction angle $\phi$ is not affected by changes in bed elevation. Basal
topography is derived from the ETOPO1 combined topography
and bathymetry dataset with a~resolution of 1\,arc-min \citep{data:etopo1}.

@@

Atmospheric forcing of the model consists of a present-day monthly climatology
modified by a lapse-rate correction and time-dependent temperature offsets. The
present-day climatology was computed from the near-surface air temperature and
precipitation rate fields of the North American Regional Reanalysis (NARR) over
the period xxxx--xxxx (Fig.~\ref{fig:atm}). Modern climate of the North
American Cordillera is characterised by strong geographic variations of
seasonality, timing of the precipitation peak and daily temperature variability.
Our choice of data from the NARR is motivated by the need for an accurate,
high-resolution precipitation forcing, as outlined in a previous sensitivity
study.

Temperature offset time-series are reconstructed from proxy records from
the Greenland Ice Core Project (GRIP), the North Greenland Ice Core Project
(NGRIP), the European Project for Ice Coring in Antarctica (EPICA), the Lake
Vostok ice core, and Ocean Drilling Program (ODP) sites 1012 and 1020, both
located off the Californian shore. Palaeo-temperatures from the GRIP and NGRIP
records were calculated using a quadratic equation \aref:

\todo{add equation here,}

while temperature reconstructions from the Antarctic and oceanic cores was
provided by their authors. In addition, all records were scaled linearly in
order to simulate comparable ice volumes and realistic ice extents at the last
glacial maximum (Table~\ref{tab:records}, Fig.~\ref{fig:timeseries}).

Prior to surface mass balance computation, the model dynamically applies
a~lapse-rate correction to surface air temperature. This correction accounts
for the evolution of ice thickness on the one hand, and differences between the
climate forcing reference topography and the ice flow model basal topography on
the other hand. It uses a~reference topography distinct from the modelled basal
topography and specific to each climate forcing dataset.
An annual lapse rate of 6\,\unit{{\degree}C\,km^{-1}} is used in all
simulations.
